Syntax and Semantics of Abstract Binding Trees

### 2015-12-09 paper.tex
mention sml implementation

The contribution of this paper is the development of the syntax and semantics
of multi-sorted nominal abts, an extension of second order universal algebra to
support symbol-indexed families of operators. Additionally, we have developed
the categorical semantics for abts formally in Constructive Type Theory using
the Agda proof assistant~\cite{norell:2007}.

>>>>

The contribution of this paper is the development of the syntax and semantics
of multi-sorted nominal abts, an extension of second order universal algebra to
support symbol-indexed families of operators. Additionally, we have developed
the categorical semantics for abts formally in Constructive Type Theory using
the Agda proof assistant~\cite{norell:2007}; we have also developed an
implementation for abstract binding trees in Standard ML, which we intend to
integrate into the JonPRL proof assistant \cite{jonprl:2015}.
